CIVILITY: Cloud based Interactive Visualization of Tractography Brain Connectome

### 2016-07-11 doc/spiePaper/article.tex
DOC : add equations,

\graphicspath{{../images/}}

@@

We compute the average of the brain connectome at each year (Figure 1 and Figure 2). We threshold the plotting between : 0.01 and 0.4 for a better visualization.
Figures 3 and 4 show the average of brain connectome on brain template with the same threshold.

\begin{figure}
\centering 
\subfigure[]{\includegraphics[width=8cm]{average_1y.png}}
\subfigure[]{\includegraphics[width=8cm]{average_2y.png}}
\caption[Average brain connectome at 1 (a) and 2 (b) year old]{Average brain connectome at 1 and 2 year old}
\label{fig:AverageBrainConnectome}
\end{figure}

\begin{figure}
\centering 
\subfigure[]{\includegraphics[width=15cm]{average_brainTemplate_1y.png}}
\subfigure[]{\includegraphics[width=15cm]{average_brainTemplate_2y.png}}
\caption[Average brain connectome at 1 and 2 year old]{Average brain connectome at 1 and 2 year old}
\label{fig:AverageBrainConnectomeBrainTemplate}
\end{figure}

Results show ....

\subsection{Variability of the brain connectome}

We compute the unbiased sample variance to ....

\begin{figure}
\centering 
\subfigure[]{\includegraphics[width=15cm]{variance_1y.png}}
\subfigure[]{\includegraphics[width=15cm]{variance_2y.png}}
\caption[Variability of brain connectome at 1 and 2 year old]{Average brain connectome at 1 and 2 year old}
\label{fig:VariabilityBrainConnectome1YearOld}
\end{figure}

>>>>

\graphicspath{{images/}}

@@

We compute on our dataset the average brain connectome at each year : 1 and 2 years.

\begin{equation}
	A_{i,j} = \frac{\sum_{i=0}^n M_i}{n}
	\label{equ:average}
\end{equation}

Equation \ref{equ:average} define the average brain connectome for n matrices.

We threshold the plotting between : 0.01 and 0.4 for a better visualization.
The connectivity visualized is computed with the average value between the lower and upper triangles of the connectivity matrix.

\begin{figure}
\centering 
\subfigure[]{\includegraphics[width=8cm]{average_1y.png}}
\subfigure[]{\includegraphics[width=8cm]{average_2y.png}}
\caption[Average brain connectome at 1 (a) and 2 (b) year old using the circle plotting ]{Average brain connectome at 1 (a) and 2 (b) year old using the circle plotting}
\label{fig:AverageBrainConnectome}
\end{figure}

Figure \ref{fig:AverageBrainConnectome} is the circle plotting of the average brain connectome of our dataset. Figures \ref{fig:AverageBrainConnectomeBrainTemplate} shows the average brain connectome on brain template with the same threshold.

\begin{figure}
\centering 
\subfigure[]{\includegraphics[width=8cm]{average_brainTemplate_1y.png}}
\subfigure[]{\includegraphics[width=8cm]{average_brainTemplate_2y.png}}
\caption[Average brain connectome at 1 (a) and 2 (b) year old on brain templates ]{Average brain connectome at 1 (a) and 2 (b) year old on brain templates }
\label{fig:AverageBrainConnectomeBrainTemplate}
\end{figure}

First, we visualized that the shape of the connectivity is very similar at both ages. However some links are missing in the brain connectome for 1 year old subject. Moreover, the connectivity is lower for 1 year old children compare to 2 year children.

\subsection{Variability and deviation of the brain connectome}

We compute the unbiased sample variance  (equation \ref{equ:unbiasedSampleVariance}) to show the variability of the brain connectome in a dataset.

\begin{equation}
	V_{i,j} = \frac{1}{n-1} * \sum_{i=0}^n {(M_{i,j} - A_{i,j})^2}
	\label{equ:unbiasedSampleVariance}
\end{equation}

We also compute the standard deviation of this dataset at 1 and 2 year old (equation \ref{equ:standardDeviation}).

\begin{equation}
	D_{i,j} = \sqrt{V_{i,j}}
	\label{equ:standardDeviation}
\end{equation}

Deviation threshold : 0.2 0.05

Figure shows the variabilty

\begin{figure}
\centering 
\subfigure[]{\includegraphics[width=8cm]{variance_1y.png}}
\subfigure[]{\includegraphics[width=8cm]{variance_2y.png}}
\caption[Variability of brain connectome at 1 (a) and 2 (a) year old using the circle plotting ]{Average brain connectome at 1 and 2 year old using the circle plotting }
\label{fig:VariabilityBrainConnectome}
\end{figure}

\begin{figure}
\centering 
\subfigure[]{\includegraphics[width=8cm]{deviation_1y.png}}
\subfigure[]{\includegraphics[width=8cm]{deviation_2y.png}}
\caption[Standard deviation of the brain connectome at 1 (a) and 2 (b) year old on brain templates ]{Standard deviation of the brain connectome at 1 (a) and 2 (b) year old on brain templates }
\label{fig:DeviationBrainConnectome}
\end{figure}
